A Kochen-Specker system has at least 22 vectors

### 2014-12-10 paper/main.tex
add draft watermark
paper: triangles!

@@

\section{An improved lower bound}
\label{sec:ilb}
Continuing the effort of Arends, Ouaknine and Wambler,
we consider another restriction.
\begin{proposition}
    A minimal Kochen-Specker graph has minimal vertex-order three.
    That is: every vertex is adjacent to at least three other vertices.
\end{proposition}
\begin{proof}
    Given a minimal Kochen-Specker graph~$G$.
    Suppose~$v$ is a vertex with order less than or equal~$2$.
    Let~$G'$ be~$G$ with~$v$ removed.
    Clearly~$G'$ is embeddable.
    Suppose~$G'$ is 010-colorable.
    Then we can extend the coloring to a coloring of~$G$ as follows.
    If~$v$ is adjacent to only one or no vertex,
    then we can color~$v$ with~$0$.
    Suppose~$v$ is adjacent to two vertices, say~$w$ and~$w'$.
    If one of~$w$ or~$w'$ is colored~$1$, we can color~$v$ with~$0$.
    If both~$w$ and~$w'$ are colored~$0$, we can color~$v$ with~$1$.
    This would imply~$G$ is 010-colorable, quod non.
    Therefore~$G'$ is a smaller
    Kochen-Specker graph, which contradicts the minimality of~$G$.
\end{proof}
There are only~${\sim}10^7$
squarefree non-isomorphic graphs on 17 vertices with minimal vertex order 3.
Even though Arends, Ouaknine and Wampler
note this restriction once,
surprisingly, they did not restrict their graph enumeration
to graphs with minimal vertex order 3.

>>>>

\usepackage{draftwatermark}

@@

\section{An improved lower bound}
\label{sec:ilb}
Continuing the effort of Arends, Ouaknine and Wambler,
we consider another restriction.
\begin{proposition}
    A minimal Kochen-Specker graph has minimal vertex-order three.
    That is: every vertex is adjacent to at least three other vertices.
\end{proposition}
\begin{proof}
    Given a minimal Kochen-Specker graph~$G$.
    Suppose~$v$ is a vertex with order less than or equal~$2$.
    Let~$G'$ be~$G$ with~$v$ removed.
    Clearly~$G'$ is embeddable.
    Suppose~$G'$ is 010-colorable.
    Then we can extend the coloring to a coloring of~$G$ as follows.
    If~$v$ is adjacent to only one or no vertex,
    then we can color~$v$ with~$0$.
    Suppose~$v$ is adjacent to two vertices, say~$w$ and~$w'$.
    If one of~$w$ or~$w'$ is colored~$1$, we can color~$v$ with~$0$.
    If both~$w$ and~$w'$ are colored~$0$, we can color~$v$ with~$1$.
    This would imply~$G$ is 010-colorable, quod non.
    Therefore~$G'$ is a smaller
    Kochen-Specker graph, which contradicts the minimality of~$G$.
\end{proof}
There are only~${\sim}10^7$
squarefree non-isomorphic graphs on 17 vertices with minimal vertex order 3.
Even though Arends, Ouaknine and Wampler
note this restriction once,
surprisingly, they did not restrict their graph enumeration
to graphs with minimal vertex order 3.
We present another considerable restriction.

\begin{proposition}\label{prop:ks-enoughtriangles}
    In a minimal Kochen-Specker graph,
        every node is part of a triangle.
\end{proposition}
\begin{proof}
    Given any graph~$G$ together with a vertex~$v$ of~$G$
        such that~$v$ is not part of a triangle.
    Let~$G'$ denote~$G$ without~$v$.
    Suppose~$G'$ is~$010$-colorable.
    Then so is~$G$, as we may extend the coloring of~$G'$
        to~$G$ by coloring~$v$ with~$0$.
    Contraposing: if~$G$ is not~$010$-colorable,
        then~$G'$ is not~$010$-colorable.
    Clearly, if~$G$ is embeddable, then so is~$G'$.
    Thus if~$G$ is Kochen-Specker, then so is~$G'$.
\end{proof}
There are only TODO squarefree non-isomorphic 
graphs on 17 vertices with minimal vertex degree 3
where every node is part of a triangle.
Unfortunately,
we could not find an efficient algorithm
to restrict the enumeration of graphs
to those where every node is part of a triangle.
